Energy Dependence of Synchrotron X-Ray Rims in Tycho's Supernova Remnant

### 2014-12-05 manuscript/paper-tycho.tex
Better vla/xray regions, manual prf fits, pipeline
Flesh out pipeline to process/analyze radio and X-ray profiles jointly
Set up basic shape analysis and manual (eyeballing) profile fits
Settle on final-ish set of VLA/xray regions, pass through pipeline
Tycho proper motions from Katsuda
Generalize azimuth angle interpolation script

Figure~\ref{fig:radio-prfs} shows extracted radio and nonthermal X-ray
($4$--$7\unit{keV}$) profiles from the plotted regions (Figure~\ref{fig:snr}),
shown in Figure~\ref{fig:radio-prfs}.  The radio profiles show a range of
morphology, including thin rims with a trough and either increasing and
decreasing emission towards the remnant interior.

>>>>

% General todo -- note that we ignore actual profile shape in xray FWHMs
% and, effects of multiple overlapping filaments, etc...

Figure~\ref{fig:radio-prfs} shows extracted radio and nonthermal X-ray
($4$--$7\unit{keV}$) profiles from the plotted regions (Figure~\ref{fig:snr}),
shown in Figure~\ref{fig:radio-prfs}.  The radio profiles show a range of
morphology, including thin rims with a trough and either increasing or
decreasing emission towards the remnant interior.
